---
title: "Optional Quiz"
author: "jbellier"
date: "14 décembre 2016"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Presentation of the project

The data come from the file company_data.csv, which gathers company data on 4 variables : x1, x2, x3 and y.
The goal of this project is to study the relationship between an outcome y and a predictor x1, to see the influence of this single varaible on the prediction of y. 

### Data load
```{r loadData}
CompanyDF <- read.csv("company_data.csv",header=TRUE)
dim(CompanyDF)
names(CompanyDF)
```

### Study of relationships between variables
In this section, we will plot the data and check the availability of the linear model. 

```{r plotData}
library(ggplot2)
g <- ggplot(CompanyDF, aes(x=x1,y=y)) + geom_point() + ggtitle("Study of influence of x1 on y")
g <- g + geom_smooth(method = "lm", colour = "blue")
g
```

Here we define a linear model between y and x1.
```{r Regression}
fit <- lm(y~x1,CompanyDF)
summary(fit)
```

We can see that the values of the outcomes y are mainly grouped along the regression line ${y=\beta_0+\beta_1*x_1}$. Furthermore, the value of ${R^2}$ is nearly 80%. This value is the ratio of the total  variation explaned by the model. This model shows that ${x_1}$ can explain most of the values of ${y}$. So we can say to the president of the company that there is a meaningful relationship between ${x_1}$ and  ${y}$.

### Value of the estimated coefficient between ${x_1}$ and ${y}$

We just need to take the value of the column ***Estimate*** on the line defining ${x_1}$ : 

```{r SlopeCoef}
coefs <- summary(fit)$coefficients
coefs[2,1]
```


### 95% Confidence interval for slope ${\beta_1}$
By definition, the 95% confidence interval is built on the value of the estimate and the standard error of the slope. 
```{r ConfInt_Slope}
IC_beta1 <- coefs[2,1]+qt(0.975,fit$df-2)*c(-1,1)*coefs[2,2]
IC_beta1

coefs[2,4]
```

### p-Value for ${\beta_1}$
The p-Value is given by the fourth column of the coefs table :
```{r pValueSlope}
coefs[2,4]
```